\documentclass[11pt,letterpaper]{article}

% ---------- packages ----------
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\geometry{left=0.75in, right=0.75in, top=0.6in, bottom=0.6in}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{tabularx}
\usepackage{fancyhdr}

% ---------- colours & hyperlinks ----------
\definecolor{linkblue}{HTML}{1a0dab}
\hypersetup{colorlinks=true, linkcolor=linkblue, urlcolor=linkblue, citecolor=linkblue}

% ---------- page style ----------
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\fancyfoot[C]{\thepage}

% ---------- section formatting ----------
\titleformat{\section}{\large\bfseries\scshape}{}{0em}{}[\vspace{2pt}\titlerule]
\titlespacing*{\section}{0pt}{14pt}{6pt}
\titleformat{\subsection}{\normalsize\bfseries}{}{0em}{}
\titlespacing*{\subsection}{0pt}{8pt}{3pt}

% ---------- list settings ----------
\setlist[itemize]{nosep, left=0pt .. 1.5em, label=\textbullet}

% ---------- custom commands ----------
\newcommand{\cventry}[4]{%
  \noindent\textbf{#1}\hfill#2\\
  \textit{#3}\\
  #4\par\vspace{4pt}%
}

\newcommand{\cventryshort}[3]{%
  \noindent\textbf{#1}\hfill#2\\
  \textit{#3}\par\vspace{4pt}%
}

\newcommand{\pubentry}[4]{%
  \noindent\textbf{#1}\\
  #2\\
  \textit{#3}\hfill#4\par\vspace{6pt}%
}

\newcommand{\awardline}[2]{%
  \noindent #1 \dotfill\ #2\\[2pt]%
}

% ---------- no paragraph indent ----------
\setlength{\parindent}{0pt}

\begin{document}

% ============================================================
%                         HEADER
% ============================================================
\begin{center}
  {\LARGE\bfseries Haotong Luan}\\\vspace{4pt}
  \rule{\textwidth}{0.4pt}\\\vspace{4pt}
  Future Technology School, Shenzhen Technology University\enspace$\cdot$\enspace Shenzhen, China\\
  lht20060306@outlook.com
  \enspace|\enspace
  haotongluan.github.io
\end{center}

\vspace{-4pt}

% ============================================================
%                        EDUCATION
% ============================================================
\section{Education}

\cventryshort{Shenzhen Technology University (SZTU)}{Sept 2024 -- Present}{B.Eng.\ in Automation, Future Technology School; GPA: 83.7/100}
\quad Research focus: underactuated grippers; environment-adaptive robotic hands; mechanism design.\par\vspace{4pt}

\cventryshort{Tsinghua University -- Shenzhen X-Institute}{Sept 2025 -- Present}{P-SRT Program, Joint Training (Underactuated Robotics)}
\quad Advisor: Associate Prof.\ Wenzeng Zhang. Track: X-idea $\rightarrow$ \textbf{P-SRT (current)} $\rightarrow$ E-SRT $\rightarrow$ ORIC $\rightarrow$ SURF.\par\vspace{2pt}

% ============================================================
%                      PUBLICATIONS
% ============================================================
\section{Publications}

{\small Legend: * Corresponding author}\vspace{4pt}

\subsection{Published}

\pubentry{DPS Hand: A Dual-Parallelogram and Slot-Guided Gripper for Adaptive Grasping and Environmental Scooping}{\textbf{Haotong Luan}, Haokai Ding, Tao Yang*, Wenzeng Zhang*}{Proceedings of the 2026 IEEE 22nd International Conference on Automation Science and Engineering (CASE 2026), Shenyang, China, August 17--21, 2026.}{2026}

\pubentry{PlaceRecover: Layout-Invariant Point Cloud Recovery for Robust 3D Perception under LiDAR Placement Shifts}{Benwu Wang, Zihang Wang*, Wenkai Zhu, \textbf{Haotong Luan}, Dong Kong, Binghao Wang, Yiming Zhou, Kailin Lyu, Teng Yan, Haoyu Wang, Yaohua Liu, Qiang Zhang}{Proceedings of the 2026 IEEE/RSJ International Conference on Intelligent Robots and Systems (IROS 2026), Pittsburgh, PA, USA, September 27--October 1, 2026.}{2026}

\pubentry{CSD: Conformal Selective Diagnosis for Reliable Bearing Fault Identification Under Domain Shift}{Xi Yu, Anran Lu, Keyi Chen, \textbf{Haotong Luan}*, Yuan Gao*}{Proceedings of the 2026 IEEE International Conference on Systems, Man, and Cybernetics (SMC 2026), Bellevue, WA, USA, October 4--7, 2026. (CCF C; corresponding author)}{2026}

\pubentry{Domain-Semantic Subspace Stacking for Financial Fraud Detection}{\textbf{Haotong Luan}, Minmin Chen, Zhenhui Lin, Haokai Ding, Yiwei Sheng*}{Proceedings of the 22nd International Conference on Intelligent Computing (ICIC 2026), Toronto, Canada, July 22--26, 2026. (CCF C)}{2026}

\pubentry{An Underactuated Dual-Slide Adaptive Robotic Hand with Strong Environmental Adaptability}{\textbf{Haotong Luan}, Wenzeng Zhang*, Tao Yang*}{Proceedings of the 2025 5th International Conference on Robotics, Automation, and Artificial Intelligence (RAAI 2025), Singapore, December 18--20, 2025.}{2025}

\pubentry{An Idle-Stroke Underactuated Gripper with Independent Double-Parallelogram Linkages for Pinching and Adaptive Grasping}{Yizhe Chen, \textbf{Haotong Luan}, Haokai Ding, Wenzeng Zhang*}{Proceedings of the 2025 5th International Conference on Robotics, Automation, and Artificial Intelligence (RAAI 2025), Singapore, December 18--20, 2025.}{2025}

\pubentry{GLINT: An Idle-Stroke Grasp-and-Lift Hand for In-Hand Manipulation}{Haokai Ding, \textbf{Haotong Luan}, Tao Yang*, Wenzeng Zhang*}{Proceedings of the 2025 13th International Conference on Control, Mechatronics and Automation (ICCMA 2025), Paris, France, November 24--26, 2025.}{2025}

\subsection{Submitted / Under Review Journals}

\pubentry{Manuscript submitted to \textit{Advanced Science}}{\textbf{Haotong Luan} (first author)}{Submitted. (Interdisciplinary and materials top journal; CAS Zone 1 Top; JCR Q1)}{2026}

\pubentry{Manuscript submitted to \textit{Advanced Intelligent Systems}}{\textbf{Haotong Luan} (first author)}{Submitted. (Intelligent systems and robotics interdisciplinary top journal; JCR Q1)}{2026}

\pubentry{Manuscript submitted to \textit{IEEE Robotics and Automation Letters} (RA-L)}{\textbf{Haotong Luan} (first author)}{Submitted. (Robotics and automation top journal; JCR Q1)}{2026}

\pubentry{Manuscript under review at \textit{Scientific Reports}}{\textbf{Haotong Luan} (first author)}{Under review. (JCR Q1)}{2026}

\subsection{Patents Pending}
\begin{itemize}
  \item \textbf{3 invention patents} filed and under review.
  \item \textbf{1 utility model patent} filed and under review.
\end{itemize}

% ============================================================
%                   RESEARCH & PROJECTS
% ============================================================
\section{Research \& Projects}

\cventry{Underactuated Robotic Gripper Research}{2025 -- Present}{Shenzhen X-Institute, Tsinghua University}{Designed underactuated grippers using linear-motion linkages, parallelogram mechanisms, and idle-stroke transmissions. Focus: embedding grasping logic into hardware for reliable single-actuator grasping. Led the DS Hand (first-author, RAAI 2025); collaborated on idle-stroke and GLINT gripper designs.}

\cventry{Visual-Servoing Control for Robotic-Arm Grasping}{2026 -- Present}{Shanghai AI Laboratory (Remote RA)}{Collaborating with Researcher Yuan Gao on visual-servoing control algorithms and end-effector design for robotic-arm grasping. Responsible for the mechanical gripper design mounted on the arm.}

\cventry{Quantum \& AI Winter School}{Jan 2026}{Shenzhen Loop Area Institute}{Studied generative-model-based quantum variational circuit simulation (MLP / LSTM / Transformer) under Prof.\ Peng Zhang (Tianjin University). Worked on state fidelity optimization, mixed-state simulation, and physics-constrained training.}

% ============================================================
%                       EXPERIENCE
% ============================================================
\section{Experience}

\cventryshort{P-SRT Researcher -- Shenzhen X-Institute}{Sept 2025 -- Present}{Advisor: Associate Prof.\ Wenzeng Zhang}
\quad Independently proposed the dual-slide adaptive gripper concept; conducted mechanism analysis and feasibility study, leading to long-term advising.\par\vspace{4pt}

\cventryshort{Remote Research Assistant -- Shanghai AI Laboratory}{Apr 2026 -- Present}{Supervisor: Researcher Yuan Gao}
\quad Developing visual-servoing control algorithms for robotic-arm grasping and designing the mechanical end-effector.\par\vspace{4pt}

% ============================================================
%                    HONORS & AWARDS
% ============================================================
\section{Honors \& Awards}

\awardline{\textbf{National-Level Project} (Principal Investigator), 2026 College Student Innovation and Entrepreneurship Training Program --- ``Zero-Lash Smart Grasping''}{2026}
\awardline{\textbf{Provincial-Level Project} (Member), 2026 College Student Innovation Training Program --- ``Multi-Core Fiber Dynamic Optical Trap for Single-Cell Pathology''}{2026}
\awardline{Crystal Prize for Scientific \& Technological Innovation (top 10 across SZTU)}{2025}
\awardline{Dean's Special Award for Rising Talent, Zhenxiong (Future Technology School, SZTU)}{2024--2025}
\awardline{Outstanding Student Cadre, Shenzhen Technology University}{2024, 2025}
\awardline{Excellence Prize, 15th ``Challenge Cup'' Student Entrepreneurship Competition (university round)}{2025}

% ============================================================
%                        SERVICE
% ============================================================
\section{Service \& Leadership}

\begin{itemize}
  \item \textbf{Principal Investigator}, National-Level Project ``Zero-Lash Smart Grasping'', 2026 College Student Innovation and Entrepreneurship Training Program (2026.05 -- present).
  \item \textbf{Project Member}, Provincial-Level Project on multi-core fiber dynamic optical trap for single-cell pathology, 2026 College Student Innovation Training Program (2026.05 -- present).
  \item Conference reviewer for \textbf{IEEE/RSJ IROS 2026}.
  \item Head of Organization Department, Future Technology School, SZTU (2024.12 -- present).
  \item Class Monitor \& Youth League Secretary (2024.09 -- 2025.10).
  \item Deputy Team Leader, 15th ``Challenge Cup'' Student Entrepreneurship Competition (2025).
\end{itemize}

% ============================================================
%                         SKILLS
% ============================================================
\section{Skills}

\begin{tabularx}{\textwidth}{@{} l X @{}}
\textbf{Mechanism Design:} & Parallel-jaw coupled grippers, linear linkages, parallelogram linkages, underactuated \& tendon-driven hands; SolidWorks (modeling / assembly / kinematic simulation); Bambu Lab 3D printing; rapid prototyping and grasping experiment design.\\[4pt]
\textbf{Programming:}      & Python; basic experience with deep learning frameworks (point cloud / quantum circuit simulation).\\[4pt]
\textbf{Academic Writing:}  & IEEE journal \& conference formatting; experienced with the full submission pipeline.\\[4pt]
\textbf{Languages:}         & Chinese (native); English (CET-4: 580; IELTS scheduled Dec 2026).\\
\end{tabularx}

\end{document}
